\documentclass{Report}
  
 
  
  \title{HOW TO TRANSFORM  AND INVOLVE TECHNOLOGY IN INDOOR GAMES IN MAKERERE UNIVERSITY COCIS}
  \author{ Tugumisirize Enoth 15/U/13228/PS}
  \date{20/05/2017}
  
 \begin{document}
  \maketitle
 
  
  \section{Introductionn}
Makerere university is known as center of excellency not only in technology  but also in also in sports.indoor games soon are taking over seen of sports in makerere as they donot require alot of space and many different sports can be shedulled at same time and location.\paragraph{Indoor games may include draft, ludo,chess,pool table,matatu,fifa(virtual games) among others.}
\paragraph{ most of these games involve less or no technology}
      	\subsection{ Background to the problem.}
With the increase of technology there places a need for migration from physical indoor games to softgames. due to curiosity among student they will be attracted to participate more in games . lesss participation has been noticed during indoor camps
\paragraph{ Students feel their games applications are not supported hence donot support them in turn .}
	\subsection{ Problem Statement}
The University should encourange software developers to develop softgames to mach with the desire and need of games around the campus .this encouragement should come though with facilitation as it vmotivates Students to  do so at agood pace

	\subsection{Aim and Objectives}

	\subsubsection{  General objective}
This project is to motivate the migration of the indoor games from the physical to soft game world.
The project should see the development bof  game application and availability to the students.
\subsubsection{  General objective}
The project is to attact more students to sport events.
Promote inovation among computing students.


	\subsubsection{ Project Scope}


The Games developed should run on both android os and windows as many students prefer them to other os.
Tablet ,mobile application and desktop application will be developed.
	\subsubsection{ Research Significance}
	
	
 \section{ Methodology}

 The   administration of COCIS MAKERERE UNIVERSITY will help us to motivating of students.
Through use of high level languages like C sharp,java,android etc
\begin{thebibliography}{9}
\bibitem{lamport94}
https://enoth-168114.appspot.com
\bibitem{lamport94}
https://www.newvision.co.ug/news/sports-gala

 \end{thebiblography}

  
  \end{document} 